%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{CJKutf8}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{CJK}{UTF8}{bsmi}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Hsin Yu Chen} & Email : {harry021633@gmail.com}\\
   陳昕佑 & Mobile : (+886) 901-020-267 \\
\end{tabular*}
\end{CJK}

%-----------SUMMARY-----------------
\section{Summary}
A system software engineer respecting performance and efficiency are brought by seamless integration between software and hardware. 1+ years of experience in IC verification,  platform performance enhancement and memory utilization reduction.

%-----------PROFESSIONAL SKILL-----------------
\section{Professional skills}
  \begin{itemize}[leftmargin=*] \itemsep=-3pt 
    \item {TODO}
  \end{itemize}

%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Airoha}{Hsinchu, Taiwan}
      {System Software Engineer @ Ethernet SoC team}{Feb 2022 -- Present}
      \resumeItemListStart
        \resumeItem{FreeRTOS SDK Implementation}
          {Refine the GPIO and I2C driver, eliminating the database to reduce memory usage approximate 10\%.}
        \resumeItem{Linux SDK Implementation}
          {Integrated the I2C and GPIO driver with a standard Linux subsystem, enabling it to utilize Linux-provided APIs. Additionally, I implemented a kernel module ioctl interface to reduce the frequency of user space to kernel space transitions, enhancing the boot-up speed of the program within the SDK 40\%.}
        \resumeItem{SDK Integration}
          {Redesigned and consolidated multiple SDK architectures into a single repository for enhanced maintainability and reduced development complexity. Furthermore, I refine the Makefile and redesign the compilation procedure, improving the compilation speed about 7 times.}
        \resumeItem{IC Verification}
          {Verify CPU peripherals, including I2C, GPIO, pinmux, CPU Bus.}
        \resumeItem{Debug Development}
          {}
        \resumeItem{System Level Testing Software Development}
          {Verify CPU peripherals, including I2C, GPIO, pinmux, CPU Bus.}
      \resumeItemListEnd

    \resumeSubheading
      {Side Projects}{Taipei, Taiwan}
      {}{}
      \resumeItemListStart
        \resumeItem{Vector ISA}
          {Research on conventional and modern vector architectures, including Cray vector supercomputers, RISC-V Vector Extension and ARM Scalable Vector Extension.}
        \resumeItem{Vector Microarchitecture}
          {Design a Cray-like vector core and construct a performance model on it. Evaluate the impact of vector chaining on several processor configurations.}
        \resumeItem{Code Optimization for Vector}
          {Research on effective code optimization techniques, such as loop transforms and instruction scheduling, on different vector core configurations.}
        \resumeItem{Application Profiling and Performance Projection}
          {Extract vectorizable parts of program by using LLVM, including SPEC2017fp and Darknet, and give an estimated evaluation on our vector core.}
      \resumeItemListEnd

    \resumeSubheading
      {Andes Technology Corporation}{Hsinchu, Taiwan}
      {Summer Intern @ RD/Architecture team}{Jul 2018 -- Aug 2018}
      \resumeItemListStart
        \resumeItem{Branch Prediction Performance Modeling}
          {Collaborating with VLSI team, evaluate the impact of different branch prediction policies on the high-end Andes RISC-V processor.}
        \resumeItem{Benchmark automatic flow development}
          {Develop an automatic benchmarking suite, including SPEC2006 and EEMBC, for performance analysis of Andes processors.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Cheng Kung University}{Tainan, Taiwan}
      {Master of Mechanical Engineering}{Sep. 2020 -- Aug. 2022}
    \resumeSubheading
      {National Central University}{Taoyuan, Taiwan}
      {Bachelor of Mechanical Engineering}{Sep. 2016 -- Jun. 2020}
  \resumeSubHeadingListEnd

%-----------OTHER EXPERIENCE-----------------
%\section{Other Experience}
%  \resumeSubHeadingListStart
%    \resumeSubheading
%      {Speaker of RISC-V Workshop Taiwan}{Hsinchu, Taiwan}
%      {Topic: "Simulation Evaluation of Chaining Implementation on RISC-V Vector Extension"}{Mar 2019}
%    \resumeSubheading
%      {Speaker of COSCUP 2018}{Taipei, Taiwan}
%      {Topic: "from Binary to Binary: How QEMU Works"}{Aug 2018}
%    \resumeSubheading
%      {Speaker of JCConf 2017}{Taipei, Taiwan}
%      {Topic: "Ahead-of-Time (AOT) compilation in Java 9"}{Sep 2017}
%  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{DCURL}
%      {This project aims to improve the most time-consuming part of blockchain, \textit{Proof-of-Work}, by exploiting Intel SIMD instructions (SSE and AVX2) on CPU and OpenCL on GPU, achieving average 1.64 speedup.}
%   \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}