%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{CJKutf8}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{CJK}{UTF8}{bsmi}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Hsin Yu Chen} & Email : {harry021633@gmail.com}\\
   陳昕佑 & Mobile : (+886) 901-020-267 \\
\end{tabular*}
\end{CJK}

%-----------SUMMARY-----------------
\section{Summary}
Experienced system software engineer in embedded systems development on Linux and FreeRTOS platforms. Skilled in driver implementation, debug mechanism development, and performance improvement.

%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {\href{https://www.airoha.com/}{Airoha}}{Hsinchu, Taiwan}
      {System Software Engineer @ Ethernet SoC team}{Feb 2022 -- Present}
      \resumeItemListStart
        \resumeItem{FreeRTOS SDK Implementation}
          {Refine the GPIO and I2C driver, eliminating the legacy database and functions to reduce memory usage approximate 10\%.}
        \resumeItem{Linux SDK Implementation}
          {Revamp I2C and GPIO drivers to replace legacy counterparts, transitioning to standard in-kernel platform subsystem. Additionally, develop a kernel module with ioctl interface to streamline communication between user space and kernel space, resulting in a 40\% improvement in boot-up speed.}
        \resumeItem{SDK Integration}
          {Overhauled the SDK architecture by consolidating multiple SDKs into a single repository, and restructured the Makefile compilation process, resulting in a sevenfold increase in compilation speed compared to previous iterations.}
        \resumeItem{IC Verification}
          {Verify CPU bus, GPIO, I2C, SCU (System Control Unit), pin-mux, cache, and debug module.}
        \resumeItem{Debug Mechanism Development}
          {Develop a debug mechanism to monitor access to specific memory regions and provide the corresponding program counter at the time of access.}
         \resumeItem{Increased image download speed}
          {Enhanced flash erase sections from 4k bytes to 64k bytes, resulting in a 2x improvement in image download speed.}
        \resumeItem{System Level Testing Software Development}
          {Develop production test software to verify the basic functionality of each chip, particularly focusing on the loopback function, need to check the packet count and the correctness of packet content.}
        \resumeItem{Auto Test Software Development}
          {Develop automated testing programs to verify code correctness immediately after code submission, ensuring code accuracy.}
      \resumeItemListEnd
      \resumeSubheading
      {\href{https://hackmd.io/@zoanana990/biRISC-V}{biRISC-V Analyzation}}{Tainan, Taiwan}
      {Computer Architecture}{January 2022}
      \resumeItemListStart
        \resumeItem{Exploration of biRISC-V Processor}
          {Analyze the datapath, control, and pipeline implementation within the biRISC-V processor code. Utilized Verilator with GTKWave for validation purposes.}
        \resumeItem{Analyze dual issue pipeline}
          {Explore and identify conditions for dual-issue execution. Use GTKWave to verify the assumption.}
      \resumeItemListEnd
      \resumeSubheading
      {Performance Evaluation of Algorithms used in Linux Kernel}{Hsinchu, Taiwan}
      {Linux Kernel Internal}{January 2023}
      \resumeItemListStart
        \resumeItem{Analyze sort algorithm between heap sort in Linux Kernel and customer quick sort}
          {Under certain circumstances, the custom sorting algorithm, which combines qsort and insertion sort, demonstrates an average performance improvement of 4 times over heap sort in Linux.}
        \resumeItem{Analyze string length between Linux Kernel and GCC}
          {The strlen function provided by GCC exhibits significantly better performance compared to Linux kernel, with a speedup of 6x.}
      \resumeItemListEnd
      \resumeSubheading
      {A RISC-V System Emulator}{Hsinchu, Taiwan}
      {Contribution on Github}{January 2023}
      \resumeItemListStart
        \resumeItem{Improved emulator image loading time}
          {Implemented mmap for direct mapping of linux images, reducing copying overhead, conserving memory space and enhance the bootup speed.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-------------EDUCATION------------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Cheng Kung University}{Tainan, Taiwan}
      {Master of Mechanical Engineering}{Sep. 2020 -- Aug. 2022}
    \resumeSubheading
      {National Central University}{Taoyuan, Taiwan}
      {Bachelor of Mechanical Engineering}{Sep. 2016 -- Jun. 2020}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}